The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-07-29 borel-regularity.tex
Use explicit moving point instead of dot in some integrals

% hideable to-do notes and brainstorming
\newif\ifshowtodo
\showtodofalse
\ifshowtodo
\newenvironment{todo}{\color{Coral}}{\color{black}}
\newenvironment{brainstorm}{\color{BlueViolet}\begin{itemize}}{\end{itemize}\color{black}}
\else
\NewEnviron{todo}{\iffalse\expandafter\BODY\fi}
\NewEnviron{brainstorm}{\iffalse\expandafter\BODY\fi}
\fi

@@

In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}. For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\begin{todo}[``the mathematical physics of rainbows and glories'']\end{todo}. \begin{todo}The formalism of wave optics can also be applied to the scattering of quantum particles---for example, in the ``nuclear optical model'' [Knoll--Schaeffer]. [This inspired Voros's work in ``The return of the quartic oscillator'']\end{todo} In the path integral picture of quantum mechanics, which draws inspiration from wave optics, infinite-dimensional thimble integrals are supposed to give the expectation values of observable quantities. In this context, the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value. For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas. Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}. Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimesion~\cite{gukov-marino-purtrov-resurgence,Witten}. Other examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}. \begin{todo}[\textbf{V} Is it true that all thimble integrals describes instantions? Can we have (higher dimensional) thimble integrals describing renormalons?]\end{todo}

@@

\begin{scope}[shift={(5.5, 0)}]
\begin{fiber}
\fill[pwbeige!30, draw=pwbeige!60] (-\phase-\spread:\dis) +(-\phase-\spread-90:\rshade) -- +(0, 0) arc (-\phase-\spread:-\phase+\spread:\dis) -- ++(-\phase+\spread+90:\rshade) -- (\rshade, \rshade) -- (\rshade, -\rshade) -- (0, -\rshade) -- cycle;
\genfibercontent[dual]
%%\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$\Lambda$};
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{scope}
\end{tikzpicture}
\captionof{figure}{A sector $\Omega_\alpha$ in the position domain, and the corresponding union of half-planes $\widehat{\Omega}_\alpha^\Lambda$ in the frequency domain.}\label{fig:sectorial_domain-pos-fre}
\end{center}
Let $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the function that measures distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space.

We will often make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough. Since restriction gives an inclusion $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \hookrightarrow \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^{\Lambda'})$ whenever $\Lambda < \Lambda'$, we can define a colimit space $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\bullet)$ that all of the spaces $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ include into. \begin{todo}[\textbf{A} improve definition; \textbf{V} is this definition descriptive enough?]\end{todo}
\begin{todo}\par
[Cite \cite{sternin1995borel} better for the theorem. Note that these results don't depend on which cotangent fiber we're mapping into. $\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.]
\end{todo}
%
\begin{prop}[following~\cite{sternin1995borel}]\label{prop:laplace-cont}
Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less. For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, with a norm of at most $\Gamma(\sigma)$.
\end{prop}
\begin{proof}
Given some $\phi \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta_\alpha, 0}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
\end{align*}
where $c_{z, \theta}$ is the cosine of $\arg(z) + \theta$. When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta|$ grows. This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta \phi$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$. It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta \phi$ match where their domains overlap. We can therefore glue these functions together into one big Laplace transform of $\phi$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.

We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta \phi$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$. This keeps $\Lambda - c_{z, \theta}|z|$ equal to $\Delta$, the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. It follows that
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta_\alpha, 0}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
\end{align*}
The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$. We can evaluate it by observing that it is a Laplace transform integral, with the roles of position and frequency played by $t$ and $\Delta$ respectively:
\[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
In terms of the metric on $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ defined above, this bound says that
\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
which is what we wanted to show.
\end{proof}
\begin{prop}\label{prop:inverse_laplace_analytic}
Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$. Choose any $\Lambda' > \Lambda$. Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
has a continuous left inverse
\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon), \]
with a norm of at most
\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
\end{prop}
\begin{proof}
Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$. Choosing some $\Lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$. 
%
The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\newcommand{\dis}{1.25}
\renewcommand{\phase}{0}
\newcommand{\spread}{30}

@@

Taylor expansion and summation form a two-way link between holomorphic functions and formal power series. For regular enough functions, the formal Laplace transform preserves a one-way vestige of this link: it turns Taylor expansions on the position domain into asymptotic expansions on the frequency domain. \begin{todo}[Compare with Sokal's version of the Watson--Nevanlinna theorem?]\end{todo}
\begin{lemma}\label{lem:laplace-bridge}
Let $\Omega$ be an open sector with $\zeta = 0$ at its tip, and an opening angle of $\pi$ or less\begin{todo}, as illustrated on the position-domain side of Figure~\ref{fig:sectorial_domain-pos-fre} [is it really that helpful to have a picture of this?]\end{todo}. Take some $\rho \in (-1,\infty)$. If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$.
\end{lemma}
\begin{remark}
This result is similar to Theorem~5.20 of \cite{diverg-resurg-i}. It is weaker in that it does not establish Gevrey asymptoticity, but stronger in that it can be applied to functions with fractionally shifted Taylor expansions.
\end{remark}
\begin{proof}
By adding points within the disk around $\zeta = 0$ where $\series{\varphi}$ converges, expand $\Omega$ to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, Figure~\ref{fig:domain_Upsilon}. Write $\series{\varphi}$ out in the form
\[ \series{\varphi} = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + a_2 \frac{\zeta^{\rho+2}}{\Gamma(\rho+3)} + a_3 \frac{\zeta^{\rho+3}}{\Gamma(\rho+4)} + \ldots, \]
observing that
\[ \series{\Phi} = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \frac{a_2}{z^{\rho+3}} + \frac{a_3}{z^{\rho+4}} + \ldots. \]
For each $n \in \Z_{\ge 0}$, define the tail sum $\varepsilon_n \in \singexp{\sigma+n}{\Lambda}(\Upsilon)$ by the equation
\[ \varphi = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + \ldots + a_{n-1} \frac{\zeta^{\rho+n-1}}{\Gamma(\rho+n)} + \varepsilon_n. \]
Taking the Laplace transform of both sides, we learn that
\[ \Phi = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \ldots + \frac{a_{n-1}}{z^{\rho+n}} + E_n, \]
where $E_n = \laplace_{\zeta, 0}^\theta \varepsilon_n$. To show that $\Phi$ is asymptotic to $\series{\Phi}$, we just need to prove that $|z^{\rho+n} E_n| \to 0$ as $|z| \to \infty$ along every ray.

@@

\begin{todo}[\textbf{A} define $\widehat{\Omega}_\alpha^\bullet$]\end{todo} of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.

@@

Since the series $\series{\psi}_\alpha$ lies in $\zeta^{\tau_\alpha-1} \C\{\zeta\}$, the function $\hat{\psi}_\alpha$ lies in $\zeta^{\tau_\alpha-1} \mathcal{O}(\Omega_\text{near})$. Since $\Omega_\text{near}$ is bounded, this implies that $\hat{\psi}_\alpha$ lies in $c \zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\text{near})$, where $c$ is the leading coefficient of $\series{\psi}_\alpha$. We know from Theorem~4 of \cite{reg-sing-volterra} that the equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has unique solution in the $\zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha)$. The same theorem applies on the domain $\Omega_\text{near}$, where its uniqueness provision shows that $\hat{\psi}_\alpha$ and $c\psi_\alpha$ must match. This means, in particular, that $\hat{\psi}_\alpha$ can be analytically continued throughout $\Omega_\alpha$, and it is uniformly of exponential type on that sector. Thus, $\hat{\psi}_\alpha$ has a well-defined Laplace transform along any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$, meaning that $\series{\Psi}_\alpha$ is Borel summable along any such ray. Recalling how the solution $\Psi_\alpha$ was constructed in Theorem~\ref{re:thm:exist_uniq_ODE}, we see that the Borel sum of $\series{\Psi}_\alpha$ is $c\Psi_\alpha$.

@@

\begin{todo}[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]\end{todo}

>>>>

% hideable to-do notes and brainstorming
\newif\ifshowtodo
\showtodotrue
\ifshowtodo
\newenvironment{todo}{\color{Coral}}{\color{black}}
\newenvironment{brainstorm}{\color{BlueViolet}\begin{itemize}}{\end{itemize}\color{black}}
\else
\NewEnviron{todo}{\iffalse\expandafter\BODY\fi}
\NewEnviron{brainstorm}{\iffalse\expandafter\BODY\fi}
\fi

@@

In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}. For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\cite{rainbows+glories}. \begin{todo}The formalism of wave optics can also be applied to the scattering of quantum particles---for example, in the ``nuclear optical model'' [Knoll--Schaeffer]. [This inspired Voros's work in ``The return of the quartic oscillator'']\end{todo} In the path integral picture of quantum mechanics, which draws inspiration from wave optics, infinite-dimensional thimble integrals are supposed to give the expectation values of observable quantities. In this context, the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value. For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas. Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}. Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimesion~\cite{gukov-marino-purtrov-resurgence,Witten}. Other examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}. \begin{todo}[\textbf{V} Is it true that all thimble integrals describes instantions? Can we have (higher dimensional) thimble integrals describing renormalons?]\end{todo}

@@

\begin{scope}[shift={(5.5, 0)}]
\begin{fiber}
\fill[pwbeige!30, draw=pwbeige!60] (-\phase-\spread:\dis) +(-\phase-\spread-90:\rshade) -- +(0, 0) arc (-\phase-\spread:-\phase+\spread:\dis) -- ++(-\phase+\spread+90:\rshade) -- (\rshade, \rshade) -- (\rshade, -\rshade) -- (0, -\rshade) -- cycle;
\genfibercontent[dual]
%%\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$\Lambda$};
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{scope}
\end{tikzpicture}
\captionof{figure}{A sector $\Omega_\alpha$ in the position domain, and the corresponding union of half-planes $\widehat{\Omega}_\alpha^\Lambda$ in the frequency domain.}\label{fig:sectorial_domain-pos-fre}
\end{center}
Let $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the function that measures distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space. \begin{todo}[Explain more why we write in terms of the distance function $\Delta$]\end{todo}

To make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough, it is helpful to have a space that encompasses $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ for all $\Lambda$. Since restriction gives an inclusion $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \hookrightarrow \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^{\Lambda'})$ whenever $\Lambda < \Lambda'$, we can define a colimit space $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\bullet)$ that all of the spaces $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ include into. \begin{todo}[\textbf{A} Put this definition into its own block]\end{todo}
\begin{todo}\par
[Cite \cite{sternin1995borel} better for the theorem. Note that these results don't depend on which cotangent fiber we're mapping into. $\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.]
\end{todo}
%
\begin{prop}[following~\cite{sternin1995borel}]\label{prop:laplace-cont}
Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less. For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, with a norm of at most $\Gamma(\sigma)$.
\end{prop}
\begin{proof}
Given some $\phi \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta_\alpha, 0}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
\end{align*}
where $c_{z, \theta}$ is the cosine of $\arg(z) + \theta$. When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta|$ grows. This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta \phi$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$. It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta \phi$ match where their domains overlap. We can therefore glue these functions together into one big Laplace transform of $\phi$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.

We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta \phi$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$. This keeps $\Lambda - c_{z, \theta}|z|$ equal to $\Delta$, the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. It follows that
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta_\alpha, 0}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
\end{align*}
The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$. We can evaluate it by observing that it is a Laplace transform integral, with the roles of position and frequency played by $t$ and $\Delta$ respectively:
\[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
In terms of the metric on $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ defined above, this bound says that
\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
which is what we wanted to show.
\end{proof}
\begin{prop}\label{prop:inverse_laplace_analytic}
\begin{todo}[\textbf{A} Correct proof, and possibly remove constant]\end{todo} Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$. Choose any $\Lambda' > \Lambda$. Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
has a continuous left inverse
\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon), \]
with a norm of at most
\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
\end{prop}
\begin{proof}
Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$. Choosing some $\Lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$. 
%
The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\newcommand{\dis}{1.25}
\renewcommand{\phase}{0}
\newcommand{\spread}{30}

@@

Taylor expansion and summation form a two-way link between holomorphic functions and formal power series. For regular enough functions, the formal Laplace transform preserves a one-way vestige of this link: it turns Taylor expansions on the position domain into asymptotic expansions on the frequency domain. \begin{todo}[Compare with Sokal's version of the Watson--Nevanlinna theorem?]\end{todo}
\begin{lemma}\label{lem:laplace-bridge}
Let $\Omega$ be an open sector with $\zeta = 0$ at its tip, and an opening angle of $\pi$ or less. Take some $\rho \in (-1,\infty)$. If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$.
\end{lemma}
\begin{remark}
This result is similar to Theorem~5.20 of \cite{diverg-resurg-i}. It is weaker in that it does not establish Gevrey asymptoticity, but stronger in that it can be applied to functions with fractionally shifted Taylor expansions.
\end{remark}
\begin{proof}
By adding points within the disk around $\zeta = 0$ where $\series{\varphi}$ converges, expand $\Omega$ to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, Figure~\ref{fig:domain_Upsilon}. Write $\series{\varphi}$ out in the form
\[ \series{\varphi} = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + a_2 \frac{\zeta^{\rho+2}}{\Gamma(\rho+3)} + a_3 \frac{\zeta^{\rho+3}}{\Gamma(\rho+4)} + \ldots, \]
observing that
\[ \series{\Phi} = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \frac{a_2}{z^{\rho+3}} + \frac{a_3}{z^{\rho+4}} + \ldots. \]
For each $n \in \Z_{\ge 0}$, define the tail sum $\varepsilon_n \in \singexp{\sigma+n}{\Lambda}(\Upsilon)$ by the equation
\[ \varphi = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + \ldots + a_{n-1} \frac{\zeta^{\rho+n-1}}{\Gamma(\rho+n)} + \varepsilon_n. \]
Taking the Laplace transform of both sides, we learn that
\[ \Phi = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \ldots + \frac{a_{n-1}}{z^{\rho+n}} + E_n, \]
where $E_n = \laplace_{\zeta, 0}^\theta \varepsilon_n$. To show that $\Phi$ is asymptotic to $\series{\Phi}$, we just need to prove that $|z^{\rho+n} E_n| \to 0$ as $|z| \to \infty$ along every ray.

@@

of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.\begin{todo} Cite the definition rather than the Section\end{todo}

@@

\begin{todo}[Confirm that we should have $\zeta_\alpha$ rather than $\zeta$ here]\end{todo} Since the series $\series{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \C\{\zeta_\alpha\}$, the function $\hat{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \mathcal{O}(\Omega_\text{near})$. Since $\Omega_\text{near}$ is bounded, this implies that $\hat{\psi}_\alpha$ lies in $c \zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\text{near})$, where $c$ is the leading coefficient of $\series{\psi}_\alpha$. We know from Theorem~4 of \cite{reg-sing-volterra} that the equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has unique solution in the $\zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha)$. The same theorem applies on the domain $\Omega_\text{near}$, where its uniqueness provision shows that $\hat{\psi}_\alpha$ and $c\psi_\alpha$ must match. This means, in particular, that $\hat{\psi}_\alpha$ can be analytically continued throughout $\Omega_\alpha$, and it is uniformly of exponential type on that sector. Thus, $\hat{\psi}_\alpha$ has a well-defined Laplace transform along any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$, meaning that $\series{\Psi}_\alpha$ is Borel summable along any such ray. Recalling how the solution $\Psi_\alpha$ was constructed in Theorem~\ref{re:thm:exist_uniq_ODE}, we see that the Borel sum of $\series{\Psi}_\alpha$ is $c\Psi_\alpha$.

@@
